---
title: "FY2019 Search February 2019"
author: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(salesforcer)
library(knitr)
library(RForcecom)
```


```{r cars}
username <- "christine.iyer@maine.edu"
password <- "1Edithandoliver"
securityToken <- "iFhpXgaXnuP3L5PQr69Zw2yOy"
instanceURL <- "https://login.salesforce.com/"
apiVersion <- "44.0"

#auth <- sf_auth(username = username, password = password, security_token = securityToken,
  #login_url = getOption("https://login.salesforce.com/"))



session <- sf_auth(username, password, securityToken, instanceURL, apiVersion)
```

```{r}
#sf_auth()
```

```{r}

username <- "christine.iyer@maine.edu"
password <- "1EdithandoliveriFhpXgaXnuP3L5PQr69Zw2yOy"
#securityToken <- ""
instanceURL <- "https://na24.salesforce.com/"
apiVersion <- "44.0"





session <- rforcecom.login(username, password, instanceURL,apiVersion  ) 
```










```{r use this}
my_soql <- sprintf("SELECT Id,
                           CreatedDate,
                           Email, 
                           FirstName, 
                           LastName,
                           TargetX_SRMb__Status__c, TargetX_SRMb__Student_Type__c,
                           TargetX_SRMb__Anticipated_Start_Term__c,
                           TargetX_SRMb__Anticipated_Start_Term_Year__c, 
                           App_Application_Date__c,  
                           TargetX_SRMb__Gender__c,  
                           TargetX_SRMb__Last_Data_Input_Source__c,                                                                Initial_Source_Date__c, 
                           Initial_Referral_Source__c, 
                           Recruiting_Category__c,
                           Ref__c, 
                           Primary_State_Code__c
                           
                    FROM Contact 
                    WHERE DAY_ONLY(CreatedDate) > 2019-02-05 AND DAY_ONLY(CreatedDate) < 2019-02-07 AND TargetX_SRMb__Status__c != 'Lead' 
                    AND Recruiting_Category__c != ' '")

queried_records <- sf_query(my_soql)
#kable(head(queried_records))
# dim(queried_records)
# queried_records
# unique(queried_records$Ref__c)
```
 
__College Board Juniors: Anticipated Start Fall 2020__

```{r}
LeadsUploaded <- read.csv("file:///C:/Users/christine.iyer/Box/Salesforce/Winter 2019/Conversions Winter 2019/Funnel_2-8-19.csv", header = T, stringsAsFactors = F)

# LeadsUploaded %>% group_by(Email) %>% summarise(n = n()) %>% filter(n>1)

# Leads Purchased
Geo <- c("In-State", "Out-of-State")
Leads <- c(4091, 6640)
leadsDF <- data.frame(Geo, Leads)
# Leads Uploaded
# head(LeadsUploaded)
# dim(LeadsUploaded)
# leadsDF



trythis <- merge(LeadsUploaded, queried_records, by = "Email" )
trythis <- trythis %>% mutate(DateCollected = Sys.Date())


# Don't forget to change the date!

write.csv(trythis, "file:///C:/Users/christine.iyer/Box/Salesforce/Winter 2019/Conversions Winter 2019/Conversion_04-06-20_DeDuped.csv")
# trythis %>% 
#   #filter(Student.Stage == "Lead") %>% 
#   mutate(Name = paste0(Last.Name, ", ", First.Name)) %>% 
#   group_by(Student.Stage,TargetX_SRMb__Status__c,  Email, Created.Date, Ref__c, Recruiting_Category__c,Recruiting.Category) %>% summarise(n = n())



# trythis %>% 
#   #filter(Student.Stage == "Lead") %>% 
#   #mutate(Name = paste0(Last.Name, ", ", First.Name)) %>% 
#   group_by(Student.Stage,TargetX_SRMb__Status__c,  Email, Created.Date, Ref__c, Recruiting_Category__c,Recruiting.Category) %>% summarise(n = n())
```










```{r}


trythis1 <- trythis %>% group_by(Primary_State_Code__c) %>% summarise(Inqs = n())
```


```{r}
Inqs <- trythis1 %>% mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-Of-State")) %>% group_by(Geo) %>% summarise(Inqs = sum(Inqs))

```

```{r}
Apps <- trythis %>% filter(TargetX_SRMb__Status__c == "Applicant") %>% group_by(Primary_State_Code__c) %>% summarise(Apps = n())
```


```{r}
Apps <- Apps%>% mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-Of-State")) %>% group_by(Geo) %>% summarise(Apps = sum(Apps))

```


```{r}
# LeadsUploaded %>% mutate(Recruiting.Category_Geo = ifelse(Recruiting.Category == "PJRIG", "In-State", "Out-of-State" )) %>% group_by(Recruiting.Category_Geo) %>% summarise(n = n())
```


As of April 3, 2020, the FY19 February lead name conversions are as follows: 

```{r}
new <- cbind.data.frame(leadsDF, Inqs, Apps)

new <- new[, c(1,2,4,6)]
kable(new %>% 
        mutate() %>% 
        group_by(Geo) %>% 
        summarise(
          Leads = sum(Leads), 
          Inqs = sum(Inqs),
          Apps = sum(Apps),
          InquiryYield = paste0(round(sum(Inqs)/sum(Leads)*100,2), "%"),
          AppYield = paste0(round(sum(Apps)/sum(Leads)*100,2), "%")
                     ) %>% 
        mutate(Leads = prettyNum(Leads, big.mark = ",")))

```

In February 2019, USM purchased ~10,000 lead names from the College Board, all Juniors with an anticipated start of September 2020. Confirmations and enrollments will be available in the next few months. 
<br>

__College Board Juniors: Anticipated Start Fall 2021__

<br>

In February 2020, USM purchased ~75,000 lead names, over half of which were College Board Juniors. An email search campaign began almost three weeks ago, and to date, 2 emails have been sent to these lead names. The inquiry and application conversions to date are shown below. These numbers will change daily as the campaign runs. 


```{r}

#__FY20 YTD Comparison__

#Updated: `r Sys.Date()` after 2 Email sends

FY20 <- read.csv("C:/Users/christine.iyer/Box/Search/FY19_Search/Search_February2019/FY20ConversionsCompare.csv", header = T, stringsAsFactors = F)

kable(FY20) 
      # %>% group_by(Geo) %>% 
      #   summarise(
      #     Leads = sum(as.numeric(gsub(",","", Leads))), 
      #     Inqs = sum(Inquiries),
      #     Apps = sum(Apps),
      #     InquiryYield = paste0(round(sum(Inqs)/sum(Leads)*100,2), "%"),
      #     AppYield = paste0(round(sum(Apps)/sum(Leads)*100,2), "%")
      #                ) %>% 
      #   mutate(Leads = prettyNum(Leads, big.mark = ","))
      
# 
               
```

